My Cool Title

### 2019-05-04 paper.tex

\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{amsmath}
\usepackage{subcaption}
\usepackage{caption}

@@

\begin{figure}
  \begin{subfigure}{0.5\textwidth}
    \centering
    \includegraphics[width=0.9\textwidth]{figures/boxplot_time_to_target.png}
    \caption{A set of boxplots comparing the time to target. }\label{fig:boxplot-time}
  \end{subfigure}
  \begin{subfigure}{0.5\textwidth}
    \centering
    \includegraphics[width=0.9\textwidth]{figures/cumplot_time_to_target.png}
    \caption{A set of CDFs comparing the time to target. }\label{fig:cum-time}
  \end{subfigure}
  \caption{A set of boxplots and CDFs comparing the time it took the participants to find the targets for each experiments. }
\end{figure}

>>>>

\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{amsmath}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.7\textwidth]{figures/boxplot_time_to_target.png}
  \caption{A set of boxplots comparing the time to target. }\label{fig:boxplot-time}
\end{figure}
\begin{figure}
  \centering
  \includegraphics[width=0.7\textwidth]{figures/cumplot_time_to_target.png}
  \caption{A set of CDFs comparing the time to target. }\label{fig:cum-time}
\end{figure}
